### 2017-06-02 paper/lexicographic.tex
expanded the proof of LexRSM soundness

Now since $\genRunSet_{\infty}=M_1,\dots,M_n$, there must be $1\leq j \leq n$ 
s.t. $\probm(M_j)>0$. For each $\omega\in M_j$ there is the smallest number
$i_{\omega,j}\in\Nset_0$ such that for all $i\geq i_{\omega,j}$ it holds 
$\levelrank{\omega}{i}\geq 
j$. Denote by $S_{j,i}$ the set of all $\omega$'s in $M_j$ s.t. 
$i_{\omega,j}=i$. 
Since $M_j = M_{j,1} \cup M_{j,2} \cup M_{j,3} \cup \cdots$, there is $i\in 
\Nset_0$ 
s.t. 
$\probm(M_{j,i})>0$. Continuing on the same note, for each $B\in \Nset$ we 
denote by $M_{j,i}^{B}$ the set off all $\omega$'s in $M_{j,i}$ s.t. 
$\vecseq{X}{i}{j}(\omega)\leq B$. Since $M_{j,i}= M_{j,i}^{1} \cup M_{j,i}^{2} 
\cup M_{j,i}^{3} \cup \cdots  $, there is $B\in \Nset$ s.t. 
$\probm(M_{j,i}^{B})>0$.

>>>>

Now since $\genRunSet_{\infty}=M_1,\dots,M_n$, there must be $1\leq j \leq n$ 
s.t. $\probm(M_j)>0$. For each $\omega\in M_j$ there is the smallest number
$i_{\omega,j}\in\Nset_0$ such that for all $i\geq i_{\omega,j}$ it holds 
$\levelrank{\omega}{i}\geq 
j$. Denote by $S_{j,i}$ the set of all $\omega$'s in $M_j$ s.t. 
$i_{\omega,j}=i$. 
Since $M_j = M_{j,1} \cup M_{j,2} \cup M_{j,3} \cup \cdots$, there is $i\in 
\Nset_0$ 
s.t. 
$\probm(M_{j,i})>0$. Continuing on the same note, for each $B\in \Nset$ we 
denote by $M_{j,i}^{B}$ the set off all $\omega$'s in $M_{j,i}$ s.t. 
$\vecseq{X}{i}{j}(\omega)\leq B$. Since $M_{j,i}= M_{j,i}^{1} \cup M_{j,i}^{2} 
\cup M_{j,i}^{3} \cup \cdots  $, there is $B\in \Nset$ s.t. 
$\probm(M_{j,i}^{B})>0$. Denote $p=\probm(M_{j,i}^{B})$.

Let $D$ be the set of all $\omega\in \Omega$ such that 
$\vecseq{X}{i}{j}(\omega)\leq B$. Note that $M_{j,i}^{B} \subseteq D$ and $D\in 
\genfilt_i$ (and thus also $D\in \genfilt_{i'}$ for all $i'\geq i$). 
Define a stopping time $\tilde{\stime}$ as follows: for all $\omega \in \Omega$ 
we put 
$\tilde{\stime}(\omega)=\inf\{k\in \Nset_0 \mid k\geq i \text{ and }
\levelrank{\omega}{k} < j \}$.

Define a 
(one-dimensional) stochastic process $\{\tilde{X}_k\}_{k=0}^{\infty}$ as 
follows:
$$
\tilde{X}_k(\omega) = \begin{dcases}
0 & \text{if $\omega \not\in D$}\\
B & \text{if $\omega \in D$ and $k<i$ }\\
\vecseq{X}{k}{j}(\omega) & \text{ if $k\geq i$ and $\tilde{\stime}(\omega)>i$ 
}\\
\vecseq{X}{\tilde{\stime}(\omega)}{j}(\omega) & \text{ if $k\geq i$ and 
$\tilde{\stime}(\omega)\leq i$ }.
\end{dcases}
$$

We prove several properties of the process $\{\tilde{X}_k\}_{k=0}^{\infty}$. 
First, for all $k\geq 0$, $\tilde{X}_k(\omega)\geq K$, where $K<0$ is the 
number 
such that $\vec{X}_j(\omega)\geq K$ for all $j$ and $\omega$ (such a number 
exists from the definition of LexRSM). Second, denote by 
%\begin{enumerate}
%\
%\end{itemize}
%\end{enumerate}
